Simulation Study of Angular Resolution of a New Electromagnetic Sampling Calorimeter

### 2022-02-19 paper.tex
update

\documentclass[jkps,preprint,fleqn,showpacs,showkeys]{revtex4}

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{lineno}
\usepackage{xspace}
\usepackage{cleveref}
\usepackage{stackengine}
\usepackage {xcolor}

@@

\begin{document}
\setcounter{page}{0}
\title[]{Simulation Study of Angular Resolution of a New Electromagnetic Sampling Calorimeter}

\author{YoungJun \surname{Kim}}
\author{Jung Keun \surname{Ahn}}
\affiliation{Department of Physics, Korea University, Seoul 02841}
\author{Junlee \surname{Kim}}
\email{junlee.kim@cern.ch}
\author{Eun-Joo \surname{Kim}}
\email{ejkim@jbnu.ac.kr}
\affiliation{Department of Physics education, Jeonbuk National University, Jeonju 54896}
\author{GeiYoub  \surname{Lim}}
\affiliation{IPNS/KEK Tsukuba, Japan 305-0801}

@@

\end{abstract}

%\pacs{68.37.Ef, 82.20.-w, 68.43.-h}
\keywords{Electromagnetic Calorimeter, Geant4, XGBoost, KOTO}
\maketitle

@@

\begin{acknowledgments}
\end{acknowledgments}

>>>>

\documentclass[preprint,12pt,times,a4paper]{elsarticle}

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{lineno}
\usepackage{xspace}
\usepackage{lipsum}
\usepackage{cleveref}
\usepackage{stackengine}
\usepackage{titlesec}
\usepackage {xcolor}
\usepackage[bitstream-charter]{mathdesign}
\usepackage[T1]{fontenc}
\usepackage{geometry, float}
\geometry{a4paper}

\usepackage[normalem]{ulem}
\usepackage{stackengine}

\journal{Nuclear Instruments and Methods in Physics Research A}

@@

\begin{document}

\begin{frontmatter}

\setcounter{page}{0}
\title{Simulation Study of Angular Resolution of a New Electromagnetic Sampling Calorimeter}

\author[jbnu]{Junlee~Kim\corref{cor1}}
\ead{junlee.kim@cern.ch}
\cortext[cor1]{Corresponding author. Tel.: +82-xxxxxxxxx.}
\author[jbnu]{Eun-Joo~Kim\corref{cor2}}
\ead{ejkim@jbnu.ac.kr}

\author[korea]{Young~Jun~Kim}
\author[korea]{Jung~Keun~Ahn}

\cortext[cor2]{Corresponding author. Tel.: +82-xxxxxxxxx.}
\author[kek]{Gei~Youb~Lim}

\address[jbnu]{Division of Science Education, Jeonbuk National University, Jeonju 54896, Korea}
\address[korea]{Department of Physics, Korea University, Seoul 02841, Korea}
\address[kek]{Institute of Particle and Nuclear Studies (IPNS), High Energy Accelerator Research Organization (KEK), Tsukuba 305-0801, Japan}

@@

\end{abstract}
\begin{keyword}
% keywords here, in the form: keyword \sep keyword
Electromagnetic Calorimeter \sep Geant4 \sep XGBoost \sep KOTO
\end{keyword}

\end{frontmatter}

@@

\section*{Acknowledgement}
This paper was supported by the National Research Foundation of Korea (NRF) grants funded by the Korea government (MIST) (2019R1A2C1084552 and 2020R1A3B2079993).
